Code Publishing Tutorial

### 2025-02-12 index.qmd
Clarify requirements

While the general principles taught in this tutorial apply to most researchers
publishing code, we will make very specific suggestions what tools to use.

In particular, we will assume you have installed
[Git](https://git-scm.com/downloads),
[R](https://cloud.r-project.org/),
[RStudio](https://posit.co/download/rstudio-desktop/#:~:text=2%3A%20Install%20RStudio),
and [Quarto](https://quarto.org/docs/download/).
Windows users may additionally need
[RTools](https://cloud.r-project.org/bin/windows/Rtools/).

>>>>

While the general principles taught in this tutorial apply to most researchers
publishing code, we will focus on the programming language R
and the publishing system Quarto.

To follow the tutorial you need to have installed
[Git](https://git-scm.com/downloads),
[R](https://cloud.r-project.org/), and
[Quarto](https://quarto.org/docs/download/).
Windows users may additionally need [RTools](https://cloud.r-project.org/bin/windows/Rtools/).
Some things will be explained using the [RStudio IDE](https://posit.co/download/rstudio-desktop/#:~:text=2%3A%20Install%20RStudio),
but you are free to use any IDE you like.
